\section{The CMS detector and event reconstruction}
\label{sect:CMSRec} 
The central feature of the CMS apparatus is a superconducting solenoid of 6\unit{m} 
internal diameter that provides a magnetic field of 3.8\unit{T}. Within the solenoid 
volume are a silicon pixel and strip tracker, a lead tungstate crystal electromagnetic 
calorimeter, and a brass and scintillator hadron calorimeter, each composed of a barrel 
and two endcap sections. Muons are measured in gas-ionization detectors embedded in the 
steel flux-return yoke outside the solenoid. Extensive forward calorimetry complements the coverage provided by the barrel and endcap detectors. 
A more detailed description of the CMS detector, together with a definition of the coordinate system used 
and the relevant kinematic variables, can be found in Ref. \cite{Chatrchyan:2008zzk}.

To be recorded for further study, events from pp interactions must satisfy criteria imposed by a two-level trigger system.
The first level of the CMS trigger system, composed of custom hardware processors, uses information from the 
calorimeters and muon detectors to select the most interesting events in a fixed time interval of less than 4\mus. 
The high-level trigger processor farm further decreases the event rate from around 100\unit{kHz} to less than 1\unit{kHz} 
before data storage \cite{Khachatryan:2016bia}.

The particle-flow (PF) algorithm~\cite{CMS-PAS-PFT-09-001,CMS-PAS-PFT-10-001} reconstructs and identifies each 
individual particle with an optimized combination of information from the various elements of the CMS detector. 
Jets are reconstructed from the PF candidates with the anti-$k_t$ clustering
algorithm~\cite{Cacciari:2008gp} using a distance parameter of 0.5.
We apply corrections dependent on transverse momentum (\pt) and pseudorapidity ($\eta$) 
to account for residual effects of nonuniform detector response~\cite{Chatrchyan:2011ds}.
A correction to account for multiple pp collisions within the same or nearby
bunch crossings (pileup interactions) is estimated on an event-by-event basis using the
jet area method described in Ref.~\cite{Cacciari:2007fd}, and is
applied to the reconstructed jet \pt.
The combined secondary vertex algorithm~\cite{Chatrchyan:2012jua} is used to identify (``b tag'') jets 
originating from b quarks.  This algorithm  is based on the reconstruction of secondary vertices, together with track-based lifetime information. 
In this analysis a working point is chosen such that, for jets with a \PT value greater than 60\GeV 
the efficiency for tagging a jet containing a b quark is 70\% with a light-parton jet misidentification rate of 1.5\%, 
and $\cPqc$ quark jet misidentification rate of 20\%.
Scale factors are applied to the simulated events to reproduce the tagging efficiencies measured in data, 
separately for jets originating from b or $\cPqc$ quarks, and from light-flavor partons.
Jets with  \PT $>$ 40\GeV and $\abs{\eta} < 5.0$ and b-tagged jets with \PT $>$ 20\GeV and $\abs{\eta} < 2.4$ are considered in this analysis.

The PF candidates are used to reconstruct the missing transverse momentum  vector \ptvecmiss, 
defined as the negative of the vector sum of the transverse momenta of all PF candidates.  
For each event, \MPT is defined as the magnitude of \ptvecmiss.

Hadronically decaying $\tau$ leptons are reconstructed using the hadron-plus-strips algorithm~\cite{Khachatryan:2015dfa}.
The constituents of the reconstructed jets are used to identify individual $\tau$ lepton decay modes with one charged 
hadron and up to two neutral pions, or three charged hadrons. 
Additional discriminators are used to separate \Tau from electrons and muons.
Prompt $\tau$ leptons are expected to be isolated in the detector.
To discriminate them from quantum chromodynamics (QCD) jets,
an isolation variable \cite{Khachatryan:2014wca} is defined by the scalar sum of the transverse momenta of the charged hadrons 
and photons falling within 
a cone around the $\tau$ lepton momentum direction after correcting for the effect of
pileup. The ``loose'', ``medium'', and ``tight'' working points are defined
by requiring the value of the isolation variable not to exceed 2.0, 1.0,
and 0.8 \GeV, respectively.
A similar measure of isolation is computed for charged leptons (e or $\mu$), 
where the isolation variable is divided by the \PT of the lepton. This quantity is 
used to suppress the contribution from leptons produced in hadron decays in jets.

\section{The Monte Carlo samples}
\label{sect:MCSamples}
The SUSY signal processes and SM samples, which are used to evaluate potential background contributions, 
are simulated using CTEQ6L1~\cite{Nadolsky:2008zw} parton distribution functions. 
To model the parton shower and fragmentation, all generators are interfaced with \PYTHIA 6.426~\cite{Sjostrand:2006za}.
The SM processes of $\cPZ$+jets, \wjets, $\cPqt\cPaqt$, and dibosons are generated using the \MADGRAPH 5.1~\cite{Alwall:2011uj} generator. 
Single top quark and Higgs boson events are generated with {\POWHEG} 1.0~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2009je,Alioli:2010xd}.
In the following, the events from Higgs boson production via gluon fusion, vector-boson fusion, or in association with a $\PW$ or $\cPZ$  boson 
or a \ttbar pair are referred to as ``hX.'' Later on, 
the events containing at least one top quark or one $\cPZ$ boson are referred to as ``tX'' and ``ZX,'' respectively. 
The masses of the top quark and Higgs boson are set to be 172.5\GeV~\cite{Khachatryan:2015hba} and 125\GeV~\cite{Aad:2015zhl}, respectively. Since the 
final state arising from the pair production of \PW~bosons decaying into $\tau$ leptons is very similar 
to our signal, in the following figures its contribution is shown as an independent sample labeled as ``WW.''

In one of the signal samples, pairs of charginos are produced with \PYTHIA 6.426 and decayed exclusively to the final states that contain 
two $\tau$ leptons, two $\tau$ neutrinos, and two neutralinos, as shown in Fig.~\ref{fig:Productions} (left). 
The daughter sparticle in the two-body decay of the \chione can be either a \sTau or $\sNu_{\tau}$. 
In this scenario, no decay modes are considered other than those shown in Fig.~\ref{fig:Productions} (left), so for m(\sTau) = m($\sNu_{\tau}$), the two decay chains 
(via the \sTau or $\sNu_{\tau}$) have 50\% branching fraction.
The masses of the \sTau and $\sNu_{\tau}$ are set to be equal to the mean value of the \chione and \PSGczDo masses and consequently are produced on mass shell.
If the \sTau ($\sNu_{\tau}$) mass is close to the \PSGczDo mass, the $\tau$ lepton from the \sTau (\chione) decay will 
have a low (high) momentum, resulting in a lower (higher) overall event selection efficiency, 
producing a weaker (stronger) limit on the chargino mass.
In the case where the \sTau ($\sNu_{\tau}$) mass is close to the \chione mass, the situations are opposite.
Of the scenarios in which the $\tau$ slepton and the $\tau$ sneutrino have the same mass, the scenario with the highest efficiency overall 
corresponds to the one in which these masses are half-way between the masses of the \chione and \PSGczDo.
In the other signal sample, pairs of staus are also produced with \PYTHIA 6.426, 
that decay always to two $\tau$ leptons and two neutralinos, Fig.~\ref{fig:Productions} (right). 
%To model  the parton shower and fragmentation, all generators are interfaced with \PYTHIA 6.426, which is also used to generate signal events. 
To improve the modeling of the $\tau$ lepton decays, the \TAUOLA 1.1.1a~\cite{Davidson:2010rw} package is used for both signal and background events. 

In the data set considered in this paper,
there are on average 21 pp interactions in each bunch crossing.
Such additional interactions are generated with \PYTHIA and superimposed on simulated events in a manner consistent with 
the instantaneous luminosity profile of the data set.
The detector response in the  Monte Carlo (MC) background event samples is modeled by a
detailed simulation
of the CMS detector based on {\GEANTfour}~\cite{Agostinelli:2002hh}.  
For the simulation of signal events, many samples of events, corresponding to a grid of \chione and \PSGczDo mass values, must be generated. 
To reduce  computational requirements, signal events are processed by the CMS fast simulation \cite{Abdullin:2011zz} instead of {\GEANTfour}. 
It is verified that the CMS fast simulation is in reasonable agreement with the detailed simulation for our signal which has hadronic decays of 
tau leptons in the final state.
The simulated events are reconstructed with similar algorithms used for collision data.

The yields for the simulated SM background samples are normalized to the cross sections available in the literature.
These cross sections correspond to next-to-next-to-leading-order (NNLO) accuracy for $\cPZ$+jets~\cite{Melnikov:2006kv} 
and \wjets~\cite{xsec_WZ} events. For the $\cPqt\cPaqt$ simulated samples, the cross section used is calculated to full NNLO accuracy including
the resummation of next-to-next-to-leading-logarithmic (NNLL) terms~\cite{Czakon:2011xx}.
The event yields from diboson production are normalized to the next-to-leading-order (NLO) cross section  taken from Ref.~\cite{Campbell:2011bn}. 
The \textsc{Resummino}~\cite{Fuks:2012qx,Fuks:2013vua,Fuks:2013lya} program is used to calculate the signal cross sections at NLO+NLL level where 
NLL refers to next-to-leading-logarithmic precision.
